Distance Sampling in \proglang{R}

### 2016-03-18 paper.Rmd
Updated Figure 1
See #39

```{r detectdists, fig.height=5.5, fig.width=8, echo=FALSE, message=FALSE, fig.cap="Top panels show an example detection function (left), the expected availability of objects (middle) and the resulting distribution of detections (right) for line transects. Bottom panels show an example detection function (left), the expected availability of objects (middle) and the resulting distribution of detections (right) for point transects. The distributions in the right hand plots are obtained by multiplying the detection function by the availability function and are referred to in the text as the `composite function'. \\label{fig:detectiondist}"}

opar <- par(mfrow=c(2,3))
#line and point transect examples

@@

#Line transect example
plot(x, y, xlab = "Perpendicular distance (m)", ylab = "Probability of Detection", type = "l", ylim = c(0,1.1), main = "Probability of Detection", xaxp = c(0,1,5))
line.availability <- rep(1,100)
plot(x, line.availability, xlab = "Perpendicular distance (m)", ylab = "Availability", type = "l", ylim = c(0,1.1), xlim = c(0,500), yaxt = "n", main = "Expected Availability")
plot(x,y, xlab = "Perpendicular distance (m)", ylab= "", type = "l", ylim = c(0,1.1), yaxt = "n", main = "Observed Distribution")

#Point Transect example
plot(x, y, xlab = "Radial distance (m)", ylab = "Probability of Detection", type = "l", ylim = c(0,1.1), main = "Probability of Detection", xaxp = c(0,1,5))
point.availability <- 2*pi*x
plot(x, point.availability, xlab = "Radial distance (m)", ylab = "Availability", type = "l", ylim = c(0,3300), xlim = c(0,500), yaxt = "n", main = "Expected Availability")
point.observed <- y*point.availability
plot(x, point.observed, xlab = "Radial distance (m)", ylab= "", type = "l", ylim = c(0,800), yaxt = "n", main = "Observed Distribution")

>>>>

```{r detectdists, fig.height=5.5, fig.width=9, echo=FALSE, message=FALSE, fig.cap="Top panels show an example detection function (left), the pdf of object distances (middle) and the resulting pdf of detection distances (right) for line transects. Bottom panels show an example detection function (left), the pdf of object distances (middle) and the resulting pdf of detection distances (right) for point transects. The pdf of observed detection distances in the right hand plots are obtained by multiplying the detection function by the pdf of object distances. \\label{fig:detectiondist}"}

par(mfrow=c(2,3))
#line and point transect examples

@@

set.cex  = 1
set.cex.lab = 1.2
set.cex.main = 2
#Line transect example
plot(x, y, xlab = "Perpendicular distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), xaxp = c(0,1,5), cex = set.cex, cex.lab = set.cex.lab)
line.availability <- rep(1,100)
plot(x, line.availability, xlab = "Perpendicular distance", ylab = "pdf of object distances", type = "l", ylim = c(0,1.1), xlim = c(0,500), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab, main = "Line Transect", cex.main = set.cex.main)
plot(x,y, xlab = "Perpendicular distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,1.1), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab)

#Point Transect example
plot(x, y, xlab = "Radial distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), xaxp = c(0,1,5), cex = set.cex, cex.lab = set.cex.lab)
point.availability <- 2*pi*x
plot(x, point.availability, xlab = "Radial distance", ylab = "pdf of object distances", type = "l", ylim = c(0,3300), xlim = c(0,500), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab, main = "Point Transect", cex.main = set.cex.main)
point.observed <- y*point.availability
plot(x, point.observed, xlab = "Radial distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,800), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab)
